Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-10-05 grove-paper.tex
Add graph actions to formalism with Michael and Cyrus (Eric)

A vertex $v = (u, k)$ identifies a distinct instance of the constructor $k$.
Each constructor represents a different type of node in the target language's abstract syntax tree.

A position $p$ identifies a location adjacent to some parent vertex.

@@

A graph action is a +E or -E.

Graph action semantics is a transition system
between graphs. (join with whatever it was before)

G --action--> G'

@@

>>>>

A vertex $v = (u, k)$ identifies a distinct instance of the constructor $k$.

A constructor $k \in \K$ represents a different type of node in the target language's abstract syntax tree.

A position $p \in \P$ identifies a location, adjacent to some parent vertex.

@@

We define graph edit actions as a pair of an edge state, excluding $\bot$, and an edge.
Thus, $\alpha \in \A = \left\{\Plus, \Minus\right\} \times \E$.
As a shorthand, we define $+e$ to be $(\Plus, e)$ and $-e$ to be $(\Minus, e)$.

We define the join operation $s_1 \sqcup s\_2$ to be the least upper bound of $s_1$ and $s_2$ with respect to the $\sqsubset$ ordering.
For example, $\Plus \sqcup \bot = \Plus$, which means edges can be created if they have never existed,
and $\Plus \sqcup \Minus = \Minus$, which means that once an edge is deleted it can never be restored.
%smallest element of $\Sigma$ that is greater than or equal to both $s_1$ and $s_2$.

We define the semantics of graph actions via the following
transition relation between graphs.
\[
G \overset{\left(s,e\right)}{\longrightarrow} G\left[ e \mapsto s \sqcup G(e) \right\}
\]
In other words, applying graph action $\alpha = \left(s, e\right)$ to a graph $G$
results in $G\left[e \mapsto s \sqcup G(e) \right]$ (i.e., the graph is updated at $e$ to be
the join of $s$ with whatever was already at $e$).

% Graph action semantics is a transition system between graphs.
% (join with whatever it was before)

% Intuitively, joining any edge state with $\bot$ is always the non-$\bot$ edge state (once an edge exists, it always exists).
% Joining anything with $\Minus$ is always $\Minus$ (once an edge is marked as deleted, it is permanently deleted).

@@

$G \overset{\left(e,s\right)}{\longrightarrow} G\left[ e \mapsto s \sqcup G(e) \right]$

% Edge.Map.add action.value.edge (join old_state new_state) graph
